Kid tangrams joint analysis

### 2025-11-26 code/expt_1/data_prep.Rmd
qc on transcription

# Transcript wrangle
```{r}
wrangle_transcript <- function(game_num) {
  if(file.exists(here("data/expt_1/raw_transcripts", str_c(game_num, ".csv")))){
  file = read_csv(here("data/expt_1/raw_transcripts", str_c(game_num, ".csv")))
  }
  else{
    if(file.exists(here("data/expt_1/raw_transcripts/exclude", str_c(game_num, ".csv")))){
        #file = read_csv(here("data/expt_1/raw_transcripts/exclude", str_c(game_num, ".csv")))
         file=tibble(start=NA, end=NA, text=NA, speaker=NA, trial=NA, role=NA, echo=NA, description=NA)
    }
    else{
      file=tibble(start=NA, end=NA, text=NA, speaker=NA, trial=NA, role=NA, echo=NA, description=NA)
    }
  }
  file|>
    select(start, end, text, speaker, trial, role, echo, description) |>
    fill(trial) |> 
    mutate(start = start / 1000, end = end / 1000) |>
   nest(data = c(start, end, text, speaker, trial, role, echo, description))

>>>>

# Transcript wrangle
```{r}
wrangle_transcript <- function(game_num) {
  if(file.exists(here("data/expt_1/raw_transcripts", str_c(game_num, ".csv")))){
  file = read_csv(here("data/expt_1/raw_transcripts", str_c(game_num, ".csv")))
  }
  else{
    if(file.exists(here("data/expt_1/raw_transcripts/exclude/", str_c(game_num, ".csv")))){
        file = read_csv(here("data/expt_1/raw_transcripts/exclude/", str_c(game_num, ".csv")))
        }
    else{
      file=tibble(start=NA, end=NA, text=NA, speaker=NA, trial=NA, role=NA, echo=NA, description=NA, on_topic=NA)
    }
  }
  file|>
    select(start, end, text, speaker, trial, role, echo, description,on_topic) |>
    fill(trial) |> 
    mutate(start = start / 1000, end = end / 1000) |>
   nest(data = c(start, end, text, speaker, trial, role, echo, description, on_topic))

### 2025-11-26 code/expt_3/data_prep_3.Rmd
qc on transcription

wrangle_transcript <- function(game_num) {
  if(file.exists(here("data/expt_3/raw_transcripts", str_c(game_num, ".tsv")))){
  file = read_tsv(here("data/expt_3/raw_transcripts", str_c(game_num, ".tsv")))
  }
  else{
    if(file.exists(here("data/expt_3/raw_transcripts/exclude", str_c(game_num, ".tsv")))){
        file = read_tsv(here("data/expt_3/raw_transcripts/exclude", str_c(game_num, ".tsv")))
    }
    else{
      file=tibble(start=NA, end=NA, text=NA, speaker=NA, trial=NA, role=NA, echo=NA, description=NA)
    }
  }
  file|>
    select(start, end, text, speaker, trial, role, echo, description) |>
    fill(trial) %>%
    mutate(start = start / 1000, end = end / 1000) |>
    mutate(trial = trial-1) |>
    nest(data = c(start, end, text, speaker, trial, role, echo, description))

>>>>

wrangle_transcript <- function(game_num) {
  if(file.exists(here("data/expt_3/raw_transcripts", str_c(game_num, ".tsv")))){
  file = read_tsv(here("data/expt_3/raw_transcripts", str_c(game_num, ".tsv")))
  message(game_num)
  }
  else{
    if(file.exists(here("data/expt_3/raw_transcripts/exclude", str_c(game_num, ".tsv")))){
      message(game_num)
        file = read_tsv(here("data/expt_3/raw_transcripts/exclude", str_c(game_num, ".tsv")))
    }
    else{
      file=tibble(start=NA, end=NA, text=NA, speaker=NA, trial=NA, role=NA, echo=NA,description=NA, on_topic=NA)
    }
  }
  file|>
    select(start, end, text, speaker, trial, role, echo, description, on_topic) |>
    fill(trial) %>%
    mutate(start = start / 1000, end = end / 1000) |>
    mutate(trial = trial-1) |>
    nest(data = c(start, end, text, speaker, trial, role, echo, description, on_topic))

### 2025-11-26 code/ms_analysis.Rmd
qc on transcription

transcripts |>
  filter(!is.na(trial)) |>
 filter(str_detect(speaker, "id")) |>
  filter(is.na(role)) |>
  select(expt, game, trial, text) |> View() # to check on later!!!

>>>>

transcripts |>
  filter(!is.na(trial)) |>
 filter(str_detect(speaker, "id")) |>
  filter(is.na(role)) |>
  select(expt, game, trial, text) # to check on later!!!
